Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-14 paper/paperv3.qmd
fixing more lmer > glmer errors

#h2a
surv_age_line <- lmer(
  pup_surv_int ~ age10 + (1 | animalID) + (1 | year),
  surv_recr_data
)

@@

#h2b
recr_age_line <- lmer(
  pup_recr_int ~ age10 + (1 | year),
  filter(surv_recr_data, pupsex == "F")
)

>>>>

#h2a
surv_age_line <- glmer(
  pup_surv_int ~ age10 + (1 | animalID) + (1 | year),
  surv_recr_data, 
  family = "binomial",
  control = glmerControl(optimizer = "bobyqa")
)

@@

#h2b
recr_age_line <- glmer(
  pup_recr_int ~ age10 + (1 | year),
  filter(surv_recr_data, pupsex == "F"), 
  family = "binomial",
  control = glmerControl(optimizer = "bobyqa")
)
